The Weakly Nonlinear Magnetorotational Instability

### 2016-09-02 paper/widegap_mri_paper.tex
possible ways forward in note form

\section{Discussion}
\label{sec:discussion}
In this work we carry out a formal weakly nonlinear multiscale analysis of the MRI in a Taylor Couette flow. We analyze both the standard and helical MRI, which differ only in the geometry of their imposed background magnetic fields. We find that the amplitude function, which governs the behavior of the system on long length- and timescales, obeys a real GLE for the case of the standard MRI, and a complex GLE for the helical MRI. These two systems are thus subject to different large-scale phase dynamics.

@@

This is the first weakly nonlinear analysis of the MRI in a cylindrical geometry, and the theory developed here should be compared to analytic studies of the MRI in local approximations \citep{Umurhan:2007hs,Vasil:2015}. We find that the saturation amplitude of the standard MRI scales somewhat more steeply with $\Pm$ than does this same system system in the narrow gap approximation.

The theory presented here may be extended in several ways.

>>>>

\section{Discussion}
\label{sec:discussion}
In this work we carry out a formal weakly nonlinear multiscale analysis of the MRI in a Taylor-Couette flow. We analyze both the standard and helical MRI, which differ only in the geometry of their imposed background magnetic fields. We find that the amplitude function, which governs the behavior of the system on long length- and timescales, obeys a real GLE for the case of the standard MRI, and a complex GLE for the helical MRI. These two systems are thus subject to different large-scale phase dynamics.

@@

This is the first weakly nonlinear analysis of the MRI in a cylindrical geometry, and is thus the global analogue of similar analyses in local approximations \citep{Umurhan:2007hs,Vasil:2015}. We find that the saturation amplitude of the standard MRI scales somewhat more steeply with $\Pm$ than does this same system system in the narrow gap approximation.

The theory presented here may be extended in several ways. 
- detailed comparison to specific experimental apparatus. will gle dynamics be visible? 
- the vertical dimension is incompletely modeled - stratification, etc
- explore saturation property dependence of system on rotation profile 
- different field geometries (e.g. radially varying)
- other radial boundary conditions
- drop axisymmetry
- comparison to simulation in both weakly and strongly nonlinear regimes
